### 2021-01-29 input/figdelA.tex
wip

  \draw[->] (-\X + 5pt, 0 + 2pt ) --
  node[above=-0.3em,font=\tiny]{$\ADD_{a}^{1.5}$}
  (0 - 5pt, 0 + 2pt); %% a - b
  \draw[<-] (-\X + 5pt, 0 - 2pt ) --
  (0 - 5pt, 0 - 2pt); %% b - a

  \draw[<-] (0 +5pt, 0 + 2pt) --
  node[above=-0.3em, font=\tiny]{$\ADD_{c}^{1}$}
  (\X -5pt, 0 + 2pt); %% c - b
  \draw[->] (0 +5pt, 0 - 2pt) --
  (\X -5pt, 0 - 2pt); %% b - c

@@

  \draw[<-] (\X - 3pt, 0 - 5pt) --
  (0 + 5pt, \Y + 3pt); %% d - c
  \draw[->] (\X + 3pt, 0 - 5pt) --
  node[below=-0.3em, font=\tiny, sloped]{$\ADD_{c}^{1}$}
  (0 + 5pt, \Y - 3pt); %% c - d

>>>>

  \draw[->] (-\X + 5pt, 0 + 2pt ) --
  node[above=-0.3em,font=\tiny, color=\PA]{$\ADD_{a}^{1.5}$}
  (0 - 5pt, 0 + 2pt); %% a - b
  \draw[<-] (-\X + 5pt, 0 - 2pt ) --
  (0 - 5pt, 0 - 2pt); %% b - a

  \draw[<-] (0 +5pt, 0 + 2pt) --
  node[above=-0.3em, font=\tiny, color=\PC]{$\ADD_{c}^{1}$}
  (\X -5pt, 0 + 2pt); %% c - b
  \draw[->] (0 +5pt, 0 - 2pt) --
  (\X -5pt, 0 - 2pt); %% b - c

@@

  \draw[<-] (\X - 3pt, 0 - 5pt) --
  (0 + 5pt, \Y + 3pt); %% d - c
  \draw[->] (\X + 3pt, 0 - 5pt) --
  node[below=-0.3em, font=\tiny, sloped, color=\PC]{$\ADD_{c}^{1}$}
  (0 + 5pt, \Y - 3pt); %% c - d
